%%%%%
% Jordan Conard
% Resume LaTeX Source
% jordan.conard3@gmail.com
% github.com/jconard3/resume
%%%%%

\documentclass[letterpaper]{article}
\usepackage{enumitem}

%-----Dimensions-----%
\usepackage[centering, vmargin=0.5in]{geometry}

%-----Document-----%
\begin{document}
\pagestyle{empty} % Remove page numbering
%\setlist{nolistsep} % Remove list separation


%-----Name and Contact-----%
\begin{center}
    {\Huge Jordan Conard}\\~\\
    jordan.conard3@gmail.com\\
\end{center}

%-----Objective-----%
\section*{Objective}
I am seeking new opportunities to enable others to be more secure against ever-changing security threats. I am passionate about securing emerging cloud-native technologies and developing automation to empower teams. 

%-----Work Experience-----%
\section*{Work Experience}
\begin{tabular}{l|l}
{Feb '18 - \emph{Current}} & Senior Security Operations Engineer - MailChimp, Atlanta\\
\end{tabular}
\begin{itemize}[noitemsep]
	\item Created and lead the Security Operations team to oversee defensive security in the Operations department.
	\item Designed and lead interdepartmental projects to meet security initiatives and reduce risk across the company's infrastructure.
	\item Increased collaboration and communication between Security and other Operations teams by providing subject matter expertise on new projects.
	\item Coordinated third-party penetration test engagements and lead mitigation efforts based on test report findings.
	\item Commanded security incident responses and assisted on-call teams on security issues.
\end{itemize}
\begin{tabular}{l|l}
{Jan '15 - Feb '18} & Systems Engineer - MailChimp, Atlanta\\
\end{tabular}
\begin{itemize}[noitemsep]
	\item Scaled infrastructure, monitoring and tooling to support a magnitude increase in servers over three years.
	%\item Migrated hundreds of hosted servers from Softlayer to collocated infrastructure to reduce security risk and operational expense.
	%\item Oversaw build out of a user shard from server ordering, installation and configuration, to production code deployment and QA testing.
	\item Provided on-call support for infrastructure, internal services and public facing sites.
\end{itemize}

%-----Projects-----%
\section*{Projects}
\subsubsection*{Okta Advanced Server Access Adoption for SSH Access}
\begin{itemize}[noitemsep]
	\item Enumerated shortcomings of existing Secure Shell (SSH) access solution, defined acceptance criteria for a new solution and researched potential solutions.
	\item Identified Okta Advanced Server Access (Okta ASA), a zero-trust model solution, and evaluated it through a proof-of-concept test.
	\item Lead the project team to roll ASA out company-wide and then to deprecate the previous solution.
\end{itemize}
\subsubsection*{Security Logging and Monitoring}
\begin{itemize}[noitemsep]
	\item Implemented security monitoring and alerting in Google Cloud Platform through Forseti and Cloud Security Command Center.
	\item Advised senior engineering leadership on security best practices during Google Cloud Platform (GCP) adoption.
	\item Created an Elasticsearch Security Information and Event Management (SIEM) platform to aggregate security logs from software across the company.
\end{itemize}
%\subsubsection*{Spectre/Meltdown Mitigation}
%\begin{itemize}[noitemsep]
%	\item Performed initial discovery and research of the Spectre/Meltdown vulnerabilities
%	\item Assessed risk to the infrastructure and designed the initial response project
%	\item Lead a five person project team while providing bimonthly updates to Mailchimp senior leadership
%\end{itemize}
%\subsubsection*{Home Lab}
%\begin{itemize}[noitemsep]
%	\item Created and configured a Kubernetes cluster in Google Kubernetes Engine (GKE)
%	\item Utilized the Helm package manager to install a Virtual Private Network (VPN), Hashicorp Vault and a Wordpress website
%	\item Created a repository of bootstrap scripts and Kubernetes manifests to manage the cluster and provide a backup state (https://github.com/jconard3/gcp\_k8)
%\end{itemize}
%\subsubsection*{Intro to Puppet}
%\begin{itemize}[noitemsep]
%	\item Presented a hour long lecture with evolving participatory demo (https://github.com/jconard3/puppet\_demo)
%	\item Introduced concepts of configuration management, idempotence, and declarative languages
%	\item Described puppet manifests, catalog compilation, and architecture in a typical Puppet run
%\end{itemize}
% \subsubsection*{Create a Personal VPN}
% \begin{itemize}[noitemsep]
% 	\item Fifteen minute lightning talk given during a meet-and-greet hosted by the Security team for Cyber Security Awareness Month 2018
% 	\item Showed the basic concepts of a VPN and how they can be useful for personal security
% 	\item Talked to how self-hosted VPNs can be more secure and inexpensive as paid solutions
% \end{itemize}

%-----Skills-----%
\section*{Skills}
\begin{tabular}{rl}
    Languages: & Go, Python, Bash, Puppet, C\\
    Platforms: & CentOS, Ubuntu, Google Cloud Platform, Amazon Web Services\\
    Tools: & Elasticsearch, Kubernetes, Docker, Git\\
\end{tabular}

%-----Education-----%
\section*{Education}
\begin{tabular}{rl}
    2009 - 2014 & Bachelor of Science in {Computer Engineering}\\
    & {Georgia Institute of Technology}, Atlanta\\
\end{tabular}
\end{document}